### 2023-01-23 README.rmd
Update 23 Jan

```{r}
pacman::p_load(modelsummary, gt, knitr, kableExtra, tidyverse, lubridate, tinytex, rmarkdown, crypto2, quantmod, MTS, rmgarch, rugarch, tbl2xts, fmxdat, ggthemes, summarytools, vars, tseries, pander, cowplot, qpcR, tidyquant, stargazer)

@@

sectors <- T40 %>% pull(Sector) %>% unique()
sector_return <- list()
for(i in 1:length(sectors)){
    # Loop through sectors and calculate returns and cumulative returns
    sector_return[[i]] <- portfolio_return_function(T40, sector = sectors[i]) %>% group_by(Portfolio) %>% 
      mutate(cumreturn_Rand = (cumprod(1 + Returns))) %>% # Start at 1
      mutate(cumreturn_Rand = cumreturn_Rand/dplyr:::first(cumreturn_Rand)) %>% 
      mutate(Sector = sectors[i])
}
# Rename tibbles
names(sector_return) <- sectors
sector_return
# Combine Dataframes
sectors_cum_return <- rbind(sector_return[[1]], sector_return[[2]], sector_return[[3]]) %>% arrange(date)
```

@@

```{r, results = 'asis'}
library(data.table)
star_fit.dcc <- fit.dcc@mfit$matcoef[rownames(fit.dcc@mfit$matcoef) %like% 'omega|alpha1|beta1|dcca1|dccb1',, drop = FALSE] #%>% data.frame()

@@

stargazer(star_fit.dcc,
          type = "latex",
          title = "DCC GARCH Model Fit",
          ci = TRUE,
          ci.level = 0.95,
          p.auto = TRUE,
          star.cutoffs = c(0.05, 0.01, 0.001),
          align = TRUE)

@@

stargazer(star_fit.dcc_ls,
          type = "latex",
          title = "Loadshedding DCC GARCH Model Fit",
          ci = TRUE,
          ci.level = 0.95,
          p.auto = TRUE,
          star.cutoffs = c(0.05, 0.01, 0.001),
          align = TRUE) 
```

@@

stargazer(star_fit.dcc_nls,
          type = "latex",
          title = "No Loadshedding DCC GARCH Model Fit",
          ci = TRUE,
          ci.level = 0.95,
          p.auto = TRUE,
          star.cutoffs = c(0.05, 0.01, 0.001),
          align = TRUE)
```

>>>>

```{r}
pacman::p_load(modelsummary, gt, knitr, kableExtra, tidyverse, lubridate, tinytex, rmarkdown, crypto2, quantmod, MTS, rmgarch, rugarch, tbl2xts, fmxdat, ggthemes, summarytools, vars, tseries, pander, cowplot, qpcR, tidyquant, stargazer, data.table)

@@

sectors <- T40 %>% pull(Sector) %>% unique()
sector_return <- list()
for(i in 1:length(sectors)){
    # Loop through sectors and calculate returns and cumulative returns
    sector_return[[i]] <- portfolio_return_function(T40, sector = sectors[i]) %>% group_by(Portfolio) %>% 
      mutate(cumreturn_Rand = (cumprod(1 + Returns))) %>% # Start at 1
      mutate(cumreturn_Rand = cumreturn_Rand/dplyr:::first(cumreturn_Rand)) %>% 
      mutate(Sector = sectors[i])
}
# Rename tibbles
names(sector_return) <- sectors
# Combine Dataframes
sectors_cum_return <- rbind(sector_return[[1]], sector_return[[2]], sector_return[[3]]) %>% arrange(date)
```

@@

```{r, results = 'asis'}
star_fit.dcc <- fit.dcc@mfit$matcoef[rownames(fit.dcc@mfit$matcoef) %like% 'omega|alpha1|beta1|dcca1|dccb1',, drop = FALSE] #%>% data.frame()

@@

stargazer(star_fit.dcc,
          type = "text",
          title = "DCC GARCH Model Fit",
          ci = TRUE,
          ci.level = 0.95,
          p.auto = TRUE,
          star.cutoffs = c(0.05, 0.01, 0.001),
          align = TRUE)

@@

stargazer(star_fit.dcc_ls,
          type = "text",
          title = "Loadshedding DCC GARCH Model Fit",
          ci = TRUE,
          ci.level = 0.95,
          p.auto = TRUE,
          star.cutoffs = c(0.05, 0.01, 0.001),
          align = TRUE) 
```

@@

stargazer(star_fit.dcc_nls,
          type = "text",
          title = "No Loadshedding DCC GARCH Model Fit",
          ci = TRUE,
          ci.level = 0.95,
          p.auto = TRUE,
          star.cutoffs = c(0.05, 0.01, 0.001),
          align = TRUE)
```
